Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-16 paperIEEE.tex
Fixed author line; \IEEEcompsocthanksitem seems to be necessary.
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@85 db7c848b-7755-4df2-b763-8796797afa52

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan Eilemann\thanks{email: eilemann@gmail.com} \\ %
\and Renato Pajarola~\IEEEmembership{Senior Member,~IEEE}\thanks{email:
pajarola@acm.org}}

\author{Stefan~Eilemann, David~Steiner and Renato Pajarola%
\IEEEcompsocitemizethanks{All authors are with the
Visualization and MultiMedia Lab, Department of Informatics, University of
Z\"urich.}}

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann\thanks{email: eilemann@gmail.com},
        David~Steiner\thanks{email: steiner@ifi.uzh.ch} \\ %
        and~Renato~Pajarola\thanks{email:pajarola@acm.org},~\IEEEmembership{Senior Member,~IEEE}%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem All authors are with the
Visualization and MultiMedia Lab, Department of Informatics, University of
Z\"urich.}}

%\author{Stefan Eilemann\thanks{email: eilemann@gmail.com} \\ %
%\and Renato Pajarola~\IEEEmembership{Senior Member,~IEEE}\thanks{email:
%pajarola@acm.org}}

%\author{Stefan~Eilemann, David~Steiner and Renato Pajarola%
%\IEEEcompsocitemizethanks{All authors are with the
%Visualization and MultiMedia Lab, Department of Informatics, University of
%Z\"urich.}}
